The \dealii Library, Version 9.0

### 2018-04-24 9.0/paper.tex
remove sidenote
Some minor markup improvements.

The major changes of this release are:
\begin{itemize}
\item Improved support for curved geometries;
\item Support for particle-in-cell methods;
\item Dedicated support for automatic and symbolic differentiation;
\item Interfaces to more external libraries and programs;
\item C++11 is now both required and used;
\item Support for GPU computations;
\item Support for face integrals and significant improvements of matrix-free framework;
\end{itemize}
These will all be discussed in more detail in the
following section. In addition, this release contains the following changes:
\begin{itemize}
\item \dealii has made extensive use of both the Clang-Tidy \cite{clang-tidy}
  and Coverity Scan \cite{coverity} static analysis tools for detecting bugs
  and other issues in the code. For example, around 260 issues were detected and
  fixed using the latter tool.

@@

\item Improved support for user parameters; a new \texttt{ParameterAcceptor}
  class has been added to the library. The class is intended to be used as a
  base for any class that wants to handle parameters using the
  \texttt{ParameterHandler} class. If you derive all your classes from
  \texttt{ParameterAcceptor}, and declare your parameters either with
  \texttt{parse/declare\_parameters} methods or via the
  \texttt{ParameterAcceptor::add\_parameter} method, then the declaring and
  parsing of your parameter files will be automatically managed by the
  \texttt{ParameterAcceptor::initialize} function, greatly simplifying
  the declaration and parsing of parameters in user codes.

\item New caching mechanism for expensive grid computations; We introduced a new
  class, \texttt{GridTools::Cache}, that caches computationally intensive
  information about a \texttt{Triangulation}.

This class allows the user to query some of the data structures constructed
using functions in the GridTools namespace which are computed only once, and
then cached inside this class for faster access whenever the triangulation has
not changed. The Cache is marked for update by the \texttt{Triangulation} itself
using signals.

Some of the methods in \texttt{GridTools} already use the \texttt{Cache} to
speed up repeated calls to the same expensive methods.
\item A new \texttt{MeshWorker::mesh\_loop} function has been added that
  performs the same tasks of the \texttt{MeshWorker::loop} function without
  forcing the users to adhere to a specific interface.

@@

\marginpar{All: update gmsh reference}
\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

>>>>

The major changes of this release are:
\begin{itemize}
\item Improved support for curved geometries;
\item Support for particle-in-cell methods;
\item Dedicated support for automatic and symbolic differentiation;
\item Interfaces to more external libraries and programs;
\item C++11 is now both required and used;
\item Support for GPU computations;
\item Support for face integrals and significant improvements of the matrix-free framework;
\end{itemize}
These will all be discussed in more detail in the
following section. In addition, this release contains the following changes:
\begin{itemize}
\item \dealii has made extensive use of both the Clang-Tidy \cite{clang-tidy}
  and Coverity Scan \cite{coverity} static analysis tools for detecting bugs
  and other issues in the code. For example, around 260 issues were detected and
  fixed using the latter tool.

@@

\item Improved support for user parameters: a new \texttt{ParameterAcceptor}
  class has been added to the library. The class is intended to be used as a
  base for any class that wants to handle parameters using the
  \texttt{ParameterHandler} class. If you derive all your classes from
  \texttt{ParameterAcceptor}, and declare your parameters either with
  \texttt{parse/declare\_parameters} methods or via the
  \texttt{ParameterAcceptor::add\_parameter} method, then both the
  declaration and the
  parsing of parameter files are automatically managed by
  \texttt{ParameterAcceptor::initialize}, greatly simplifying
  dealing with parameters in user codes.

\item New caching mechanism for expensive grid computations: we introduced a new
  class \texttt{GridTools::Cache} that caches computationally intensive
  information about a \texttt{Triangulation}.

This class allows the user to query some of the data structures constructed
using functions in the \texttt{GridTools} namespace. This data is then
computed only once, and
then cached inside this class for faster access whenever the triangulation has
not changed. The cache is marked for update by the \texttt{Triangulation} itself
using signals.

Some of the methods in \texttt{GridTools} already use this cache to
speed up repeated calls to the same expensive methods.
\item A new \texttt{MeshWorker::mesh\_loop} function has been added that
  performs the same tasks of the \texttt{MeshWorker::loop} function without
  forcing the users to adhere to a specific interface.

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.
